---
title: "CogScie eye-tracking lab Fall 2022"
subtitle: "Data cleaning and sanity checks"
author: "Fabio Trecca"
date: "8/12/2022"
output: html_document
---

```{r setup, include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Load in the Visual Search experiment data
```{r}
# Samples <- 
Fixations <- read_csv(file = "./Data/Fixed/Fixations.csv") 
Saccades <- read_csv(file = "./Data/Fixed/Saccades.csv")
```

# Sanity checks

The first thing we want to do is to run some sanity checks on the sample data (x and y coordinates) to make sure everything is in order. Notice anything wrong?

```{r}
## Check distribution of raw samples. Is everything alright?
hist(Fixations$PositionX)
hist(Fixations$PositionY)
hist(Fixations$PupilSize)
hist(Saccades$EndX)


```

If needed, remove artifacts and other "illegal" data points. The screen resolution at COBE Lab was 1050 x 1680. Any points outside this range should be excluded. Start by figuring out how frequent these points are. Eg. are some participants more susceptible to outliers than others?

```{r}
Fixations <- Fixations %>% 
  filter(0 < PositionX & PositionX < 1680) %>%  # Filter X-axis
  filter(0 < PositionY & PositionY < 1050) %>%  # Filter Y-axis
  filter(ParticipantID != "Jakob2")
  


Saccades <- Saccades %>% 
  filter(0 < StartX & StartX < 1680) %>%  # Filter X-axis
  filter(0 < EndX & EndX < 1680) %>%  # Filter X-axis
  filter(0 < StartY & StartY < 1050) %>%  # Filter Y-axis
  filter(0 < EndY & EndY < 1050) %>%   # Filter Y-axis
  filter(ParticipantID != "Jakob2")



```

Then filter out these outlier points:

```{r}
#Done
```


## Inspect distribution of no. of fixations and fixation duration by participant/trial both VISUALLY and NUMERICALLY

```{r}
sum_fixations <- Fixations %>% 
  group_by(ParticipantID) %>% 
  summarise(sum(FixationNo))

sum_fixations
hist(sum_fixations$`sum(FixationNo)`)
rm(sum_fixations)



mean_fixation_duration <- Fixations %>% 
  group_by(ParticipantID) %>% 
  summarise(mean(Duration))
mean_fixation_duration
hist(mean_fixation_duration$`mean(Duration)`)

```

What do you notice? Make sure that nothing looks funky in the data!

## Inspect distribution of no. of saccades and saccade amplitude by participant/trial both VISUALLY and NUMERICALLY

```{r}
sum_saccades <- Saccades %>% 
  group_by(ParticipantID) %>% 
  summarise(sum(SaccadeNo))

sum_saccades
hist(sum_saccades$`sum(SaccadeNo)`)
rm(sum_saccades)



mean_saccades_amplitude <- Saccades %>% 
  group_by(ParticipantID) %>% 
  summarise(mean(Amplitude))
mean_saccades_amplitude
hist(mean_saccades_amplitude$`mean(Amplitude)`)

```

What do you notice? Make sure that nothing looks funky in the data!

## Inspect distribution of pupil size by participant/trial both VISUALLY and NUMERICALLY

```{r}

```

What do you notice? Make sure that nothing looks funky in the data!

## Check distribution of Time variable. Is there anything weird?

```{r}

```

## Let's also do some outlier checks:

```{r}
## Check for outliers in fixation duration using a boxplot

```

```{r}
## Check for outliers in saccade length using a boxplot

```

